The non-independence of nations and why it matters

### 2022-11-28 appendix.Rmd
fix broken link in appendix
fix mean 2000km radius method in sim; start updating manuscript

---
output:
  pdf_document: default
  html_document: default
---
\renewcommand{\appendixname}{\bf{Supplementary Material}}
\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}

@@

## Supplementary Results

### Geographic and cultural phylogenetic signal estimates for Human Development Index and Inglehart's value dimensions

```{r load signal}
tar_load(c(hdiGeo, hdiLin, tradGeo, tradLin, survGeo, survLin))
```

Controlling for shared cultural ancestry, the proportion of national-level variance explained by spatial proximity was `r printnum(hdiGeo$hypothesis$Estimate, digits = 2)` for the Human Development Index (95% credible interval [`r printnum(hdiGeo$hypothesis$CI.Lower, digits = 2)` `r printnum(hdiGeo$hypothesis$CI.Upper, digits = 2)`]; $\text{BF}_{\neq0}$ > 100), `r printnum(tradGeo$hypothesis$Estimate, digits = 2)` for traditional values (95% CI [`r printnum(tradGeo$hypothesis$CI.Lower, digits = 2)` `r printnum(tradGeo$hypothesis$CI.Upper, digits = 2)`]; $\text{BF}_{\neq0}$ > 100), and `r printnum(survGeo$hypothesis$Estimate, digits = 2)` for survival values (95% CI [`r printnum(survGeo$hypothesis$CI.Lower, digits = 2)` `r printnum(survGeo$hypothesis$CI.Upper, digits = 2)`]; $\text{BF}_{\neq0}$ = `r printnum(1 / survGeo$hypothesis$Evid.Ratio, digits = 2)`). Controlling for spatial proximity, the proportion of variance explained by shared cultural ancestry was `r printnum(hdiLin$hypothesis$Estimate, digits = 2)` for the Human Development Index (95% CI [`r printnum(hdiLin$hypothesis$CI.Lower, digits = 2)` `r printnum(hdiLin$hypothesis$CI.Upper, digits = 2)`]; $\text{BF}_{\neq0}$ > 100), `r printnum(tradLin$hypothesis$Estimate, digits = 2)` for traditional values (95% CI [`r printnum(tradLin$hypothesis$CI.Lower, digits = 2)` `r printnum(tradLin$hypothesis$CI.Upper, digits = 2)`]; $\text{BF}_{\neq0}$ > 100), and `r printnum(survLin$hypothesis$Estimate, digits = 2)` for survival values (95% CI [`r printnum(survLin$hypothesis$CI.Lower, digits = 2)` `r printnum(survLin$hypothesis$CI.Upper, digits = 2)`]; $\text{BF}_{\neq0}$ > 100).

@@

```{r dag, fig.width=6, fig.height=3.5, fig.cap="(ref:dagCaption)"}
tar_read(dag)
```

@@

```{r plotSim1, fig.width=9.5, fig.height=5.5, fig.cap="(ref:plotSim1Caption)"}
tar_read(plotSim1)
```

@@

```{r plotSim2, fig.width=9.5, fig.height=5.5, fig.cap="(ref:plotSim2Caption)"}
tar_read(plotSim2)
```

@@

```{r plotReplications2, fig.width=8, fig.height=8, fig.cap="(ref:plotReplications2Caption)"}
tar_read(plotReplications2)
```

@@

```{r plotReplications3, fig.width=8.2, fig.height=6, fig.cap="(ref:plotReplications3Caption)"}
tar_read(plotReplications3)
```

@@

```{r plotReplications4, fig.width=5, fig.height=5, fig.cap="(ref:plotReplications4Caption)"}
tar_read(plotReplications4)
```

@@

Hammarström, H., Forkel, R., Haspelmath, M. & Bank, S. _Glottolog 3.0._ (Max Planck Institute for the Science of Human History, 2017). doi:[10.5281/zenodo.4061162](https://doi.org/10.5281/zenodo.4061162)

>>>>

\renewcommand{\appendixname}{\bf{Supplementary Material}}
\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}

@@

@@

```{r dag, fig.width=6, fig.height=3.5, fig.cap="(ref:dagCaption)", fig.pos='H', out.width="\\textwidth"}
tar_read(dag)
```

(ref:plotReview2Caption) _Analysis-level results from systematic review of 100 highly-cited cross-national studies of economic development (red) and cultural values (blue)._ (a) Proportion of analyses accounting for non-independence, overall and split by common methods of controlling for non-independence. (b) The association between journal impact factor and the probability that an analysis accounts for non-independence. (c) Estimated trend over time for the probability that an analysis accounts for non-independence. Point ranges represent estimated proportions and 95% credible intervals. Lines and shaded areas are posterior median regression lines and 50% credible intervals from Bayesian multilevel models. Region FEs = region fixed effects.

```{r plotReview2, fig.width=6.5, fig.height=6, fig.cap="(ref:plotReview2Caption)", fig.pos='H', out.width="\\textwidth"}
tar_read(plotReview2)
```

@@

```{r plotSim1, fig.width=9.5, fig.height=5.5, fig.cap="(ref:plotSim1Caption)", fig.pos='H', out.width="\\textwidth"}
tar_read(plotSim1)
```

@@

```{r plotSim2, fig.width=9.5, fig.height=5.5, fig.cap="(ref:plotSim2Caption)", fig.pos='H', out.width="\\textwidth"}
tar_read(plotSim2)
```

@@

```{r plotReplications2, fig.width=8, fig.height=8, fig.cap="(ref:plotReplications2Caption)", fig.pos='H', out.width="\\textwidth"}
tar_read(plotReplications2)
```

@@

```{r plotReplications3, fig.width=8.2, fig.height=6, fig.cap="(ref:plotReplications3Caption)", fig.pos='H', out.width="\\textwidth"}
tar_read(plotReplications3)
```

@@

```{r plotReplications4, fig.width=5, fig.height=5, fig.cap="(ref:plotReplications4Caption)", fig.pos='H', out.width="\\textwidth"}
tar_read(plotReplications4)
```

## Supplementary Tables

(ref:tableSignalCaption) Geographic and cultural phylogenetic signal results for economic development and cultural values variables. Signal estimates reflect the proportion of national-level variance explained by geographic and linguistic covariance matrices. Bayes Factors (BF) reflect support for the hypothesis that the signal estimate differs from zero. HDI = Human Development Index; GDPpc = gross domestic product per capita.

```{r tableSignal, echo=F, warning=F, message=F}
apa_table(
  tar_read(tableSignal),
  booktabs = TRUE,
  placement = "H",
  font_size = "small",
  caption = "(ref:tableSignalCaption)"
)
```

(ref:tableArticlesReviewCaption) List of 100 papers included in literature review, sorted by annual rate of citations since publication.

```{r tableArticlesReview, echo=F, warning=F, message=F}
apa_table(
  tar_read(tableArticlesReview),
  booktabs = TRUE,
  placement = "H",
  font_size = "small",
  longtable = TRUE,
  align = c("m{2cm}", "m{11cm}", "m{2cm}"),
  caption = "(ref:tableArticlesReviewCaption)"
)
```

@@

Hammarström, H., Forkel, R., Haspelmath, M. & Bank, S. _Glottolog 3.0._ (Max Planck Institute for the Science of Human History, 2017). doi: [10.5281/zenodo.4061162](https://doi.org/10.5281/zenodo.4061162)
